---
title: "Gene Analysis for"
output: html_notebook
---
Vectors containing vectors with the different species we have:
```{r}
names_all <- c("UniProtID","Selaginella moellendorffii", "Amborella trichopoda", "Dioscorea rotundata","Musa acuminata",
              "Zea mays","Sorghum bicolor","Setaria italica","Leersia perrieri","Oryza barthii","Oryza meridionalis",
              "Oryza glumaepatula","Oryza glaberrima","Oryza punctata","O. Sativa","Oryza indica",
              "Oryza nivara", "Oryza brachyantha","Oryza rufipogon","Oryza longistaminata","Brachypodium distachyon",
              "Aegilops tauschii", "Triticum dicoccoides","Triticum urartu","Triticum aestivum","Hordeum vulgare",
              "Beta vulgaris", "Nicotiana attenuata","Solanum lycopersicum","Solanum tuberosum", "Helianthus annuus",
              "Daucus carota","Vitis vinifera", "Lupinus angustifolius","Trifolium pratense","Medicago truncatula",
              "Vigna radiata","Vigna angularis","Phaseolus vulgaris","Glycine max","Prunus persica",
              "Manihot esculenta","Populus trichocarpa","Cucumis sativus","Brassica oleracea","Brassica rapa",
              "Brassica napus", "Arabidopsis lyrata","Arabidopsis thaliana", "Arabidopsis halleri", 
              "Corchorus capsularis","Gossypium raimondii","Theobroma cacao","Physcomitrella patens",
              "Ostreococcus lucimarinus", "Chlamydomonas reinhardtii", "Galdieria sulphuraria","Cyanidioschyzon merolae",
              "Chondrus crispus")

names_rice <- c("Oryza barthii","Oryza meridionalis", "Oryza glumaepatula","Oryza glaberrima","Oryza punctata",
               "O. Sativa","Oryza indica","Oryza nivara", "Oryza brachyantha","Oryza rufipogon","Oryza longistaminata")

names_no_rice <- c("Selaginella moellendorffii", "Amborella trichopoda", "Dioscorea rotundata","Musa acuminata",
                   "Zea mays","Sorghum bicolor","Setaria italica","Leersia perrieri","Brachypodium distachyon",
                   "Aegilops tauschii", "Triticum dicoccoides","Triticum urartu","Triticum aestivum",
                   "Hordeum vulgare","Beta vulgaris","Nicotiana attenuata","Solanum lycopersicum","Solanum tuberosum", 
                   "Helianthus annuus","Daucus carota","Vitis vinifera", "Lupinus angustifolius",
                   "Trifolium pratense","Medicago truncatula","Vigna radiata","Vigna angularis", 
                   "Phaseolus vulgaris","Glycine max","Prunus persica","Manihot esculenta","Populus trichocarpa", 
                   "Cucumis sativus","Brassica oleracea","Brassica rapa","Brassica napus",
                   "Arabidopsis lyrata","Arabidopsis thaliana", "Arabidopsis halleri", "Corchorus capsularis",
                   "Gossypium raimondii","Theobroma cacao","Physcomitrella patens",
                   "Ostreococcus lucimarinus","Chlamydomonas reinhardtii", "Galdieria sulphuraria",
                   "Cyanidioschyzon merolae", "Chondrus crispus")
names_monocots <- c("Dioscorea rotundata","Musa acuminata",
              "Zea mays","Sorghum bicolor","Setaria italica","Leersia perrieri","Oryza barthii","Oryza meridionalis",
              "Oryza glumaepatula","Oryza glaberrima","Oryza punctata","O. Sativa","Oryza indica",
              "Oryza nivara", "Oryza brachyantha","Oryza rufipogon","Oryza longistaminata","Brachypodium distachyon",
              "Aegilops tauschii", "Triticum dicoccoides","Triticum urartu","Triticum aestivum","Hordeum vulgare")

names_not_monocots <- (setdiff(names_all, names_monocots))[2:length(names_not_monocots)]
```

Next create a dataframe containing the all the genes then sort these genes by phylogeny (as presented in the names_all vector)
```{r}
library(dplyr)
library(data.table)
genes_sorted <- setcolorder(Genes, names_all)
genes_sorted <- t(genes_sorted)
colnames(genes_sorted) <- genes_sorted[1,]
genes_sorted <- as.data.frame(genes_sorted)
genes_sorted <- genes_sorted[2:59,]
```

Create two dataframes to work from, one with genes as the rows and one with species are the rows:
```{r}
species_rows <- genes_sorted
genes_rows <- as.data.frame(t(genes_sorted))
```

```{r}
gene_search <- function(arg1) {
  library(magicfor)
  magic_for()
  for (i in colnames(arg1)) {
  i_boo <- arg1[,i] %in% NA
  i_list <- arg1[i_boo]
  if (length(i_list) < 1){
    put(i)
  } 
}
output_genes <- magic_result_as_vector()
output_logical <- output_genes %in% NA
output_genes <- ouput_genes[!output_logical]  
  
}
```



Now we start identifying unique genes amongst the different classes of species

First we want to find the genes conserved across all species:
```{r}
magic_for()
for (i in colnames(species_rows)) {
  i_boo <- species_rows[,i] %in% NA
  i_list <- species_rows[i_boo]
  if (length(i_list) < 1){
    put(i)
  } 
}

conserved_genes_all <- magic_result_as_vector()
logical_all <- conserved_genes %in% NA
conserved_genes_all <- conserved_genes[!logical_all]

gene_search(species_rows)


conserved_genes_df <- species_rows[,conserved_genes_all]
```

Now we want to find genes conserved across only rice species:
```{r}
#Genes conserved across all rice
magic_for()
rice_species <- genes_rows[names_rice]
rice_species <- as.data.frame(t(rice_species))
gene_search <- function(df_of_interest)
for (i in colnames(rice_species)) {
  i_boo <- rice_species[,i] %in% NA
  i_list <- rice_species[i_boo]
  if (length(i_list) < 1){
    put(i)
  } 
}

conserved_rice_genes <- magic_result_as_vector()
logic_rice <- conserved_rice_genes %in% NA
conserved_rice_genes <- conserved_rice_genes[!logic_rice]

conserved_rice_genes_df <- species_rows[,conserved_rice_genes]

#Genes unique to only rice.
#First generate a dataframe that contains only the genes conserved in rice and that only contains species that aren't rice
conserved_rice_genes_df_no_rice <- conserved_rice_genes_df[names_no_rice,]
#Next we search this dataframe for genes that are only present in the rice (i.e. there are only NAs )
for (i in colnames(conserved_rice_genes_df_no_rice)) {
  i_boo <- conserved_rice_genes_df_no_rice[,i] %in% NA
  i_list <- conserved_rice_genes_df_no_rice[i_boo]
  if (length(i_list) == nrow(conserved_rice_genes_df_no_rice)){
    put(i)
  } 
}


```

```{r}
magic_for()
monocot_species <- genes_rows[names_monocots]
monocot_species <- as.data.frame(t(monocot_species))
for (i in colnames(monocot_species)) {
  i_boo <- monocot_species[,i] %in% NA
  i_list <- monocot_species[i_boo]
  if (length(i_list) < 1){
    put(i)
  } 
}

conserved_monocot_genes <- magic_result_as_vector()
logic_mono <- conserved_monocot_genes %in% NA
conserved_monocot_genes <- conserved_monocot_genes[!logic_mono]

conserved_mono_genes_df <- species_rows[,conserved_monocot_genes]

conserved_mono_genes_no_mono <- conserved_mono_genes_df[names_not_monocots,]

for (i in colnames(conserved_mono_genes_no_mono)) {
  i_boo <- conserved_mono_genes_no_mono[,i] %in% NA
  i_list <- conserved_rice_genes_df_no_rice[i_boo]
  if (length(i_list) == nrow(conserved_rice_genes_df_no_rice)){
    put(i)
  } 
}

```



